Ae. albopictus CPP manuscript

### 2020-07-27 Albopictus_cpp_MS.Rmd
more data

```{r message=FALSE, echo=FALSE, include=FALSE}
library("papeR")
library("flextable")
library("drc") #3.0.1
library("knitr") #1.25
library("tidyverse") #1.2.1
library("stringr") #1.4.0
library("geosphere") #1.5.10
library("lubridate") #1.7.4
library("maps")
library("mapdata")
library("ggedit")
library("ggrepel")
library("cowplot")
library("ggrepel")
library("stats")
library("ggbiplot")

@@

```{r, echo=FALSE, include=FALSE}
#GDD 400 deadline data
#importing and reshaping table
gdd400_us <- read.csv("GDD400_US.csv", check.names=FALSE) %>% gather(year, gdd400, "1998":"2018", factor_key=FALSE)
gdd400_us$year<-as.numeric(gdd400_us$year)
gdd400_jp <- read.csv("GDD400_JP.csv", check.names=FALSE) %>% gather(year, gdd400, "1998":"2018", factor_key=FALSE)
gdd400_jp$year<-as.numeric(gdd400_jp$year)
#adding latitudes
locations<-read.csv("mapping_pops_cpp_expt.csv")
gdd400_us<-left_join(gdd400_us, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_jp<-left_join(gdd400_jp, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_all<-rbind(gdd400_us, gdd400_jp)
gdd400_all$pop<-as.factor(gdd400_all$pop)
gdd400_all<-mutate(gdd400_all, interval=case_when(year<=2017 & year>=2008 ~ 'y2008-2017',
                                                  year<2008 ~ 'y1998-2007'))

@@

@@

@@

@@

```{r echo=FALSE, include=FALSE}
#FIG 4
gdd_cpp_plot_decade<-plot_grid(gdd_cpp_interval_08, gdd_cpp_interval_18, nrow=2, labels="AUTO")
#FIG S5
gdd_cpp_plot_year<-plot_grid(gdd_08, gdd_18, nrow=2, labels="AUTO")
```

@@

>>>>

```{r message=FALSE, echo=FALSE, include=FALSE}
library("papeR")
library("drc") #3.0.1
library("knitr") #1.25
library("tidyverse") #1.2.1
library("stringr") #1.4.0
library("geosphere") #1.5.10
library("lubridate") #1.7.4
library("maps")
library("mapdata")
library("ggedit")
library("ggrepel")
library("cowplot")
library("ggrepel")
library("stats")
library("ggbiplot")

@@

```{r, echo=FALSE, include=FALSE}
#GDD 400 deadline data
#importing and reshaping table
gdd400_us <- read.csv("GDD400_US.csv", check.names=FALSE) %>% gather(year, gdd400, "1998":"2018", factor_key=FALSE)
gdd400_us$year<-as.numeric(gdd400_us$year)
gdd400_jp <- read.csv("GDD400_JP.csv", check.names=FALSE) %>% gather(year, gdd400, "1998":"2018", factor_key=FALSE)
gdd400_jp$year<-as.numeric(gdd400_jp$year)
#adding latitudes
locations<-read.csv("mapping_pops_cpp_expt.csv")
gdd400_us<-left_join(gdd400_us, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_jp<-left_join(gdd400_jp, dplyr::select(locations, pop, latitude, country, only_2008), by=c("pop"))
gdd400_all<-rbind(gdd400_us, gdd400_jp)
gdd400_all$pop<-as.factor(gdd400_all$pop)
gdd400_all<-mutate(gdd400_all, interval=case_when(year<=2017 & year>=2008 ~ 'y2008-2017',year<2008 ~ 'y1998-2007'))

@@

```{r}
#photoperiods on deadline dates
PP_us <- read.csv("deadline465_pp_US.csv", check.names=FALSE) %>% gather(year, deadline_daylength, "1998":"2018", factor_key=FALSE)
PP_jp <- read.csv("deadline465_pp_jp.csv", check.names=FALSE) %>% gather(year, deadline_daylength, "1998":"2018", factor_key=FALSE)
PP_pops<-rbind(PP_us, PP_jp)
PP_pops$year<-as.numeric(PP_pops$year)
```

@@

```{r}
gdd_all_new<-left_join(gdd_all_new, PP_pops, by=c("pop","year"))
```

@@

```{r}
#CPP vs. photoperiod on deadline day
gdd_pp_08 <- ggplot(filter(gdd_all_new, year==2007, CPP_YEAR==2008), aes(x=deadline_daylength, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=22) + stat_smooth(method=lm, se=FALSE, aes(color=country), linetype="longdash") + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.75,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    xlab("2007 Deadline Day Length") + ylab("CPP (h), 2008") + ylim(12.3,14.2)

gdd_pp_18 <- ggplot(filter(gdd_all_new, year==2017, CPP_YEAR==2018), aes(x=deadline_daylength, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=21) + stat_smooth(method=lm, se=FALSE, aes(color=country)) + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.75,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
xlab("2017 Deadline Day Length") + ylab("CPP (h), 2018") + ylim(12.3, 14.2)

@@

```{r echo=FALSE, include=FALSE}
#FIG 4
gdd_cpp_plot_decade<-plot_grid(gdd_cpp_interval_08, gdd_cpp_interval_18, nrow=2, labels="AUTO")
#FIG S5
gdd_cpp_plot_year<-plot_grid(gdd_08, gdd_pp_08, gdd_18, gdd_pp_18, nrow=2, labels="AUTO")
```

@@

```{r}
sample_locations_2017<-read.csv("MeanTempUSAandJapan2017.csv") %>% gather(location, temp, "MAN":"TAK")
sample_locations_2017$UncountDegrees<-if_else(sample_locations_2017$temp<=10,sample_locations_2017$temp,10)
sample_locations_2017$CountDegrees<-if_else(sample_locations_2017$temp<=10,0,sample_locations_2017$temp-10)

sample_locations_2017_reshape <- dplyr::select(sample_locations_2017, DOY, location, CountDegrees, UncountDegrees) %>% gather(degreetype, degrees, "CountDegrees":"UncountDegrees")

sample_locations_2017_reshape$location<-factor(sample_locations_2017_reshape$location, levels=c("BRU","FAY","MAN","KAG","TAK","SEN"))

sample_locations_2017_reshape$deadline2017<-case_when(
  sample_locations_2017_reshape$location == "BRU" ~ 289,
  sample_locations_2017_reshape$location == "FAY" ~ 276,
  sample_locations_2017_reshape$location == "MAN" ~ 263,
  sample_locations_2017_reshape$location == "KAG" ~ 274,
  sample_locations_2017_reshape$location == "TAK" ~ 257,
  sample_locations_2017_reshape$location == "SEN" ~ 246,)

location_labels<-c("BRU (31.3 N)","FAY (35.03 N)","MAN (38.63 N)","KAG (31.6 N)","TAK (35.35 N)","SEN (38.29 N)")
names(location_labels)<-c("BRU","FAY","MAN","KAG","TAK","SEN")

sample_locations_gdd<-ggplot(filter(sample_locations_2017_reshape, DOY>180), aes(x=DOY, y=degrees, fill=degreetype)) +
    theme(text=element_text(size=24), legend.position="none",
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
  geom_bar(stat="identity", width=1) + 
  scale_fill_manual(values=c("dark gray","light gray")) + 
  geom_hline(yintercept=10, linetype="dashed") + 
  xlab("Ordinal Day (2017)") + ylab("Mean Daily Temp (C)") + geom_vline(aes(xintercept=deadline2017)) +
  facet_wrap(~location, labeller=labeller(location=location_labels))

```{r}
#Fig S4 two parts
gdd_examples<-plot_grid(gdd_deadline_plots, sample_locations_gdd, nrow=2, labels="AUTO")
